ITS\_LIVE: A Cloud-Native Approach to Monitoring Glaciers from Space

### 2023-10-29 paper.qmd
fix typo

Glaciers often serve as "canaries in the coalmine", responding to a warming environment well before other impacts of climate change become evident. But to benefit from Earth’s natural early-warning systems requires near-real-time monitoring of all the world’s glaciers at high spatial and temporal resolution. ITS_LIVE continuously processes, assimilates, and harmonizes data from multiple satellites and sensors including optical imagers, and synthetic aperture radars to produce a high-resolution, near-real-time picture of ice velocity worldwide. Products are available and ready to be integrated into diverse scientific workflows within days of data acquisition, and scientists have taken note, generating workflows that rely on access to near-real-time data. To date, the project has processed over a Petabyte (250 bytes) of archival satellite imagery using complex algorithms to extract the geophysical variable of interest. Such an effort is made feasible by the scalable architecture of cloud computing that provides access to tens of thousands of computational cores co-located with satellite data archives.

>>>>

Glaciers often serve as "canaries in the coalmine", responding to a warming environment well before other impacts of climate change become evident. But to benefit from Earth’s natural early-warning systems requires near-real-time monitoring of all the world’s glaciers at high spatial and temporal resolution. ITS_LIVE continuously processes, assimilates, and harmonizes data from multiple satellites and sensors including optical imagers, and synthetic aperture radars to produce a high-resolution, near-real-time picture of ice velocity worldwide. Products are available and ready to be integrated into diverse scientific workflows within days of data acquisition, and scientists have taken note, generating workflows that rely on access to near-real-time data. To date, the project has processed over a Petabyte (2^50 bytes) of archival satellite imagery using complex algorithms to extract the geophysical variable of interest. Such an effort is made feasible by the scalable architecture of cloud computing that provides access to tens of thousands of computational cores co-located with satellite data archives.

### 2023-10-29 paper.tex
fix typo

\begin{keyword}
    glaciology \sep climate change \sep big data \sep 
    cloud computing
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced]}{\end{tcolorbox}}\fi

@@

Glaciers often serve as ``canaries in the coalmine'', responding to a
warming environment well before other impacts of climate change become
evident. But to benefit from Earth's natural early-warning systems
requires near-real-time monitoring of all the world's glaciers at high
spatial and temporal resolution. ITS\_LIVE continuously processes,
assimilates, and harmonizes data from multiple satellites and sensors
including optical imagers, and synthetic aperture radars to produce a
high-resolution, near-real-time picture of ice velocity worldwide.
Products are available and ready to be integrated into diverse
scientific workflows within days of data acquisition, and scientists
have taken note, generating workflows that rely on access to
near-real-time data. To date, the project has processed over a Petabyte
(250 bytes) of archival satellite imagery using complex algorithms to
extract the geophysical variable of interest. Such an effort is made
feasible by the scalable architecture of cloud computing that provides
access to tens of thousands of computational cores co-located with
satellite data archives.

>>>>

\begin{keyword}
    glaciology \sep climate change \sep big data \sep 
    cloud computing
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, interior hidden, boxrule=0pt, enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

Glaciers often serve as ``canaries in the coalmine'', responding to a
warming environment well before other impacts of climate change become
evident. But to benefit from Earth's natural early-warning systems
requires near-real-time monitoring of all the world's glaciers at high
spatial and temporal resolution. ITS\_LIVE continuously processes,
assimilates, and harmonizes data from multiple satellites and sensors
including optical imagers, and synthetic aperture radars to produce a
high-resolution, near-real-time picture of ice velocity worldwide.
Products are available and ready to be integrated into diverse
scientific workflows within days of data acquisition, and scientists
have taken note, generating workflows that rely on access to
near-real-time data. To date, the project has processed over a Petabyte
(2\^{}50 bytes) of archival satellite imagery using complex algorithms
to extract the geophysical variable of interest. Such an effort is made
feasible by the scalable architecture of cloud computing that provides
access to tens of thousands of computational cores co-located with
satellite data archives.
